SMT-Boosted Security Types and Correctness for Low-Level MPC

### 2025-12-11 toplas26/examples.tex
yet another update

\subsection{Evaluation}
We have implemented the $\metaprot$ language and automated Hoare logic
using an Antlr parser and Scala backend with cvc5 Java bindings for
interaction with proof engines.  To evaluate
performance, we have written and verified gate libraries
using the GMW protocol for binary circuits as excerpted in
Figure \ref{fig-gmwprepost} in Section \ref{section-metalang}, and for
passive and malicious secure arithmetic circuits using Beaver Triple
multiplication as presented in Figures \ref{fig-beaver} and
\ref{fig-beaver-bdoz} in this Section.  We have considered field sizes
typically used to encode binary, 16 bit, 32 bit, and 64 bit
integers.

In addition to libraries, we have verified 2, 8, and 64-bit vector
zero-test GMW circuits containing 3, 15, and 127 gates respectively,
based on ``Bristol Fashion'' circuits \cite{bristol}. By verified, we
mean automated verification of the zero-test specification expressed
as a \ttt{postcondition}. We considered both the cvc5 Bit-Vector and
Satisfiability Modulo Finite Fields (SMFF) theories as proof engines
for these binary circuits.

Results are presented in Figure \ref{fig-preludetest}. We found that
verification of library components was efficient even up to large
field sizes. Verification of the zero-test circuits revealed a clear
performance advantage for the Bit-Vector theory, which verified
the 64-bit zero test in GMW in less than 7 seconds. In contrast,
it took several minutes to verify even the small 2-bit zero-test
circuit in SMFF, and larger circuits took too long to consider
for a practical evaluation. In all cases, the SMT-based approach
supported categorically better performance
than can be achieved using previous brute-force methods developed for
$\fieldp{2}$ and binary circuits \cite{skalka-near-ppdp24}.

>>>>

\subsection{Evaluation}
We have implemented the $\metaprot$ language and automated Hoare logic
using an Antlr parser and Scala backend with cvc5 Java bindings for
interaction with proof engines.  To evaluate performance, we have
written and verified gate libraries using the GMW protocol for binary
circuits as excerpted in Figure \ref{fig-gmwprepost} in Section
\ref{section-metalang}, and for passive and malicious secure
arithmetic circuits using Beaver Triple multiplication as presented in
Figures \ref{fig-beaver} and \ref{fig-beaver-bdoz} in this Section.
We have considered field sizes typically used to encode binary, 16
bit, 32 bit, and 64 bit integers. Results are presented in Figure
\ref{fig-preludetest}. We found that verification of library
components was efficient even up to large field sizes. Since typing is
compositional (see, e.g., Figure \ref{fig-beaver-types}), verification
of gate properties relevant to \emph{security} will scale to larger
circuits.

Circuit \emph{correctness} also benefits from compositional
verification-- for example, the correctness of a GMW ``and'' gate (as
in Figure \ref{fig-gmwprepost}) only needs to be proven once, though
instantiated and integrated into the whole-program analysis needed to
verify a large circuit specification. We have verified 2, 8, and
64-bit vector zero-test GMW circuits containing 3, 15, and 127 gates
respectively, based on ``Bristol Fashion'' circuits \cite{bristol}. By
verified, we mean automated verification of the zero-test
specification expressed as a \ttt{postcondition}. We considered both
the cvc5 Bit-Vector and Satisfiability Modulo Finite Fields (SMFF)
theories as proof engines for these binary circuits.

Verification of the zero-test circuits was efficient in the Bit-Vector
theory, which verified the 64-bit zero test in GMW in less than 7
seconds. However, it took several minutes to verify even the small
2-bit zero-test circuit in SMFF, and larger circuits took too long to
consider for a practical evaluation. This could be attributed to the
relative maturity of the Bit-Vector theory as compared to SMFF.  In
any case, the SMT-based approach achieves categorically better
performance than previous brute-force methods developed for binary
circuits \cite{skalka-near-ppdp24}.
